Presentation Title

### 2017-08-21 thesis/chapters/ch1-intro.tex
Thanks Johan

In Bitcoin's case, the consensus algorithm is called \emph{proof-of-work}.
Where miners (parties that run the Bitcoin network) collect transactions and compete in solving a puzzle.
The puzzle is easy to verify but difficult to solve.
Only the miner that solves it can generate a valid block containing all the collected transactions.
The miner is also rewarded with new coins and transaction fees.
It is important to note that every block depends on the previous block.
Hence the name blockchain.
This property ensures malicious nodes cannot easily rewrite history if they do not have a majority of the network's computing power.
Consequently, it is unlikely for more than one blockchain to exist in the network for a long period of time.
Thus, every party sees a consistent blockchain which solves the double spending problem.
% Further, due to the reward mechanism,
% people are incentivised to act as miners and keep the system running.

Bitcoin has had its ups and downs, but overall it has grown into an enormous system.
Its power consumption is as high as Republic of Ireland~\cite{o2014bitcoin}.
Its market capitalisation, at the time of writing, is over 60 billion USD and growing (see \Cref{fig:market-cap}).
\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{market-cap}
\caption{Market capitalisation and price of Bitcoin, graph is extracted from~\cite{bitcoinmarketcap}.}
\label{fig:market-cap}
\end{figure}
Many online marketplaces are using Bitcoin.
For example, Steam\footnote{\url{https://store.steampowered.com/}} and Amazon\footnote{Not directly, but via \url{https://purse.io/}.}.
Due to its success, people from many different disciplines began investigating in ways to use blockchain technology.
This includes finance~\cite{finance}, health care~\cite{healthcare}, logistics~\cite{supplychain} and energy~\cite{energy}.

Sadly, as traditional blockchain systems began to gain popularity,
their limitations also became apparent.
Bitcoin has the infamous 7 transactions per second upper bound~\cite{vukolic2015quest}, 
which is due to the fact that blocks are fixed to 1 MB and are only generated on average every 10 minutes.
Since every Bitcoin transaction is at least 250 bytes, it computes to about 7 transactions per second.
Due to this limitation, it is not uncommon to see a long backlog of about 20,000 transactions\footnote{\url{https://blockchain.info/unconfirmed-transactions/}}.
A few months ago the backlog even reached 100,000, which meant new transactions would take at least 11 hours to be written to the blockchain~\cite{bitcoinbacklog}.
This issue has plagued the Bitcoin community for some time and is the root cause for the block size debate, which some call a civil war~\cite{bitcoincivilwar}.
Parties that are for the increase in block size argue that a larger block would improve the transaction rate.
Parties against it argue that it would make mining more centralised because blocks take longer to propagate through the network.
It also requires a hard (non-backwards compatible) fork,
which risks consensus failure and devaluation.
A recent empirical study by Croman et al.~\cite{croman2016scaling} has shown that increasing the block size or the block interval may help.
But given the bandwidth and latency constraints of today's network,
it is not possible to have more than 27 transactions per second.
To achieve transaction rates higher than that, it will lead to unfairness for nodes that do not have a good network connection.
Thus, fundamental changes are necessary to run at the scale of centralised payment processors such as Visa,
which is in the order of tens of thousands transactions per second~\cite{visa}.

The Bitcoin community understands the issue and many proposals exist with the aim to make Bitcoin more scalable.
The most prominent one is Segregated Witness or SegWit~\cite{segwit}.
It moves the signature data to the end of the block and uses a variable block size up to 4 MB.
The effect is that the first 1 MB of the block is still backwards compatible, thus there is no need for a hard fork.
It also solves the transaction malleability problem~\cite{bitcoinmalleability} which paves the way for off-chain transactions via Lightning Network~\cite{lightningnetwork}.
However, some fear SegWit is not enough and wish to see a hard fork that uses ``Adjustable Blocksize Cap'' that increase the maximum block size even further to 8 MB~\cite{bitcoincash}.
The ongoing civil war resulted in a Bitcoin fork, called Bitcoin Cash~\cite{bitcoincasharticle}.
At the time of writing, it is too early to speculate how these proposals and forks may affect the scalability properties of Bitcoin.
But the conclusion that we can draw from the scalability debate is that the Bitcoin design is fundamentally not scalable,
and it is highly non-trivial to ``patch'' the problem.

@@

Using the aforementioned insight,
we explore an alternative consensus model for blockchain systems where transactions themselves do not reach consensus,
but nevertheless verifiable at a later stage by any node in the network.
We call our system \textsc{Checo}, derived from \emph{che}ckpoint \emph{co}nsensus.
From a high level, our system works as follows.
Every node stores its own hash chain and every block contains only one transaction.
We randomly select nodes in every round, the selected ones are called facilitators.
Facilitators reach consensus not on the individual transactions,
but on the state of every chain represented by a single digest, called a checkpoint block.
If a checkpoint block of some node is in consensus, 
then that node can prove to any other node that it holds a set of transactions that compute (form a chain) to the checkpoint block.
As a result, those transactions are tamper-proof.
The key difference from the early blockchain systems is the independence of the transaction validation phase.
Prior systems such a Bitcoin and Ethereum entangled the consensus algorithm with the transaction validation, restricting performance.
By splitting this functionality we achieved horizontal scalability in the general case.
That is, by adding new nodes into the network, the global transaction rate should increase proportionally,
regardless of the choice of system parameters.

Our main contributions are the following.
\begin{itemize}
    \item We formally introduce a blockchain system---\textsc{Checo}.
        It uses individual hash chains and checkpoint blocks on every node to achieve
        horizontally scalable in the general case for the first time.
    \item We formally analyse \textsc{Checo} to ensure correctness as defined in our system architecture.
    \item We provide an implementation and then experiment with up to 1200 nodes,
        our results show strong evidence of horizontal scalability.
\end{itemize}

>>>>

In Bitcoin's case, the consensus algorithm is called \emph{proof-of-work} (PoW).
Where miners (parties that run the Bitcoin network) collect transactions and compete in solving a puzzle.
The puzzle is easy to verify but difficult to solve.
Only the miner that solves it can generate a valid block containing all the collected transactions.
The miner is also rewarded with new coins and transaction fees.
It is important to note that every block depends on the previous block.
Hence the name blockchain.
This property ensures malicious nodes cannot easily rewrite history if they do not have a majority of the network's computing power.
Consequently, it is unlikely for more than one blockchain to exist in the network for a long period of time.
Thus, every party sees a consistent blockchain which solves the double spending problem.
% Further, due to the reward mechanism,
% people are incentivised to act as miners and keep the system running.

Bitcoin has had its ups and downs, but overall it has grown into an enormous system.
Its power consumption is as high as the Republic of Ireland~\cite{o2014bitcoin}.
Its market capitalisation, at the time of writing, is over 60 billion USD and growing (see \Cref{fig:market-cap}).
\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{market-cap}
\caption{Market capitalisation and price of Bitcoin, graph is extracted from~\cite{bitcoinmarketcap}.}
\label{fig:market-cap}
\end{figure}
Many online marketplaces are using Bitcoin.
For example, Steam\footnote{\url{https://store.steampowered.com/}} and Amazon\footnote{Not directly, but via \url{https://purse.io/}.}.
Due to its success, people from many different disciplines began investigating in ways to use blockchain technology.
This includes finance~\cite{finance}, health care~\cite{healthcare}, logistics~\cite{supplychain} and energy~\cite{energy}.

Sadly, as traditional blockchain systems began to gain popularity,
their limitations also became apparent.
Bitcoin has the infamous 7 transactions per second upper bound~\cite{vukolic2015quest}, 
which is due to the fact that blocks are fixed to 1 MB and are only generated on average every 10 minutes.
Since every Bitcoin transaction is at least 250 bytes, it computes to about 7 transactions per second.
Due to this limitation, it is not uncommon to see a long backlog of about 20,000 transactions\footnote{\url{https://blockchain.info/unconfirmed-transactions/}}.
A few months ago the backlog even reached 100,000, which meant new transactions would take at least 11 hours to be written to the blockchain~\cite{bitcoinbacklog}.
This issue has plagued the Bitcoin community for some time and is the root cause for the block size debate, which some call a civil war~\cite{bitcoincivilwar}.
Parties which are for an increase in block size argue that a larger block would improve the transaction rate.
Parties against it argue that it would make mining more centralised because blocks take longer to propagate through the network.
It also requires a hard (non-backwards compatible) fork,
which risks consensus failure and devaluation.
A recent empirical study by Croman et al.~\cite{croman2016scaling} has shown that increasing the block size or the block interval may help.
But given the bandwidth and latency constraints of today's network,
it is not possible to have more than 27 transactions per second.
To achieve transaction rates higher than that, it will lead to unfairness for nodes that do not have a good network connection.
Thus, fundamental changes are necessary to run at the scale of centralised payment processors such as Visa,
which is in the order of tens of thousands transactions per second~\cite{visa}.

The Bitcoin community understands the issue and many proposals exist with the aim to make Bitcoin more scalable.
The most prominent one is Segregated Witness or SegWit~\cite{segwit}.
It moves the signature data to the end of the block and uses a variable block size up to 4 MB.
The effect is that the first 1 MB of the block is still backwards compatible, thus there is no need for a hard fork.
It also solves the transaction malleability problem~\cite{bitcoinmalleability} which paves the way for off-chain transactions via the Lightning Network~\cite{lightningnetwork}.
However, some fear SegWit is not sufficient and wish to see a hard fork that uses an ``Adjustable Blocksize Cap'' that increases the maximum block size even further to 8 MB~\cite{bitcoincash}.
The ongoing civil war resulted in a Bitcoin fork, called Bitcoin Cash~\cite{bitcoincasharticle}.
At the time of writing, it is too early to speculate how these proposals and forks may affect the scalability properties of Bitcoin.
But the conclusion that we can draw from the scalability debate is that the Bitcoin design is fundamentally not scalable,
and it is highly non-trivial to ``patch'' the problem.

Moreover, Bitcoin is far from distributed.
It is more accurate to say Bitcoin is made in China~\cite{madeinchina}.
The combination of cheap electronics and electricity has made China one of the most profitable place to mine Bitcoins.
At the time of writing, China holds about 80\% of the hashing power~\cite{bitcoinpool}.
Effectively putting China in control of the 60 billion-dollar ecosystem.
If the government decides to flex its totalitarian muscles,
then it would spell the end of the ecosystem.

@@

Using the aforementioned insight,
we explore an alternative consensus model for blockchain systems where transactions themselves do not reach consensus,
but nevertheless verifiable at a later stage by any node in the network.
A verified transaction is guaranteed to be tamper-proof and irrefutable.
% We call our system \textsc{Checo}, derived from \emph{che}ckpoint \emph{co}nsensus.
% From a high level, our system works as follows.
% Every node stores its own hash chain and every block contains only one transaction.
% We randomly select nodes in every round, the selected ones are called facilitators.
% Facilitators reach consensus not on the individual transactions,
% but on the state of every chain represented by a single digest, called a checkpoint block.
% If a checkpoint block of some node is in consensus, 
% then that node can prove to any other node that it holds a set of transactions that compute (form a chain) to the checkpoint block.
% As a result, those transactions are tamper-proof.
% The key difference from the early blockchain systems is the independence of the transaction validation phase.
% Prior systems such a Bitcoin and Ethereum entangled the consensus algorithm with the transaction validation, restricting performance.
% By splitting this functionality we achieved horizontal scalability in the general case.
% That is, by adding new nodes into the network, the global transaction rate should increase proportionally,
% regardless of the choice of system parameters.
Our main contributions are the following.
\begin{itemize}
    \item We formally introduce a blockchain system---\textsc{Checo}\footnote{Derived from \emph{che}ckpoint \emph{co}nsensus.}.
        It uses individual hash chains and checkpoint blocks on every node to achieve
        horizontally scalable in the general case for the first time.
    \item We formally analyse \textsc{Checo} to ensure correctness as defined in our system architecture.
    \item We provide an implementation and then experiment with up to 1200 nodes,
        our results show strong evidence of horizontal scalability.
\end{itemize}

### 2017-08-21 thesis/chapters/ch2-problem.tex
Thanks Johan

We saw that early blockchain systems face a scalability problem.
In particular, the use proof-of-work is unlikely to reach a transaction rate suitable for ubiquitous use.
Many attempts to fix the scalability problem exist in academia as well as the industry.
In this chapter, we describe the related work in the form of a mini taxonomy and identify areas for improvement and limitations.
Then, we state our research question which aims to overcome some of the limitations.

\section{Related work and mini taxonomy}
\label{sec:taxonomy}

Blockchain research has seen a surge in recent years from both the industry and academia,
this resulted in a myriad of blockchain systems with different approaches to scalability.
To understand the current state-of-the-art,
we classify various block\-chain systems by their scalability approach,
beginning with the baseline.

\subsection{Early blockchain systems}
This category represents the baseline,
which are systems with a probabilistic consensus algorithm.
That is, transactions never reach consensus with a probability of 1.
Given sufficient computational power, adversaries are able to undo any transaction.
The typical examples are proof-of-work based systems such as Bitcoin, Ethereum and other Altcoins.
In Bitcoin, nodes compete in solving puzzles.
The first node solves the puzzle has the privilege to create a new block.
The level of consensus of a block containing many transactions is determined by how deep it is in the Bitcoin blockchain,
which is also called the number of confirmation.
The probability of a block being orphaned drops exponentially as the depth increases~\cite{bitcoin}.
Nevertheless, the probability of the highest block being orphaned is non-negligible.

The advantage of this approach is that it can be used in a large network.
In fact, prior to Bitcoin, there was no internet-scale consensus protocol.
Bitcoin is also fault-tolerant because attackers can not out pace honest users in finding new blocks unless they have a majority of the computational power,
as long as the majority is honest and reasonable measures are taken to prevent the selfish mining attack~\cite{eyal2014majority}.
The disadvantage, however, is that transactions are never in consensus with a probability of 1---no consensus finality.
Hence double spending is possible for transactions that do not have a large number of confirmations.
Furthermore, as we mentioned in the~\Cref{ch:intro},
the performance is limited due to the fact that blocks are of fixed size and are generated at fixed intervals.
Thus early blockchain systems do not scale.

@@

Off-chain transaction systems are implemented using multi-signature addresses~\cite{bitcoinmultisig} and hashed time-locked Bitcoin contracts~\cite{bitcointimelock}.
In the simplest case, 
if two parties wish to make frequent transactions,
they open a payment channel in the form of a multi-signature Bitcoin address (for two parties it would be a 2-of-2 signature address).
Each of the party must also deposit some Bitcoins in the multi-signature address,
this is called the opening transaction.
Both parties keep the channel state which is not broadcasted to the network.
The state is updated when the two parties make new transactions.
The protocol disincentivises the parties from broadcasting old channel states.
If this occurs, the counterparty can drain all the Bitcoins in the channel.
To close the channel, the parties simply broadcast the latest net settlement to the Bitcoin network,
this is called the closing transaction.
Effectively, only two transactions need to be broadcasted to the Bitcoin network---the opening and the closing transaction,
even if the two parties made thousands or millions of transactions in between.
The two-party scheme can be extended to a network of channels,
which allows two parties to make off-chain transactions without an open channel as long as they are connected by nodes that do.

@@

This category of systems uses traditional Byzantine consensus algorithms such as PBFT~\cite{castro1999practical}.
In essence, they contain a fixed set of nodes (sometimes called validating peer) that run a Byzantine consensus algorithm to decide on new blocks.
This technique is often used in permissioned system where the validators must be predetermined,
for example, Hyperledger Fabric~\cite{cachin2016architecture}.

A nice aspect of Byzantine consensus and in particular PBFT is that it can handle much more transactions than classical blockchain systems.
PBFT can, for example, achieve 10,000 TX/s if the number of validating peer is under 16~\cite[Section 5.2]{miller2016honey}.
Further, in contrast to proof-of-work, PBFT consensus is final.
That is, transaction history cannot be re-written if it is already in the blockchain.

@@

\subsection{Combining proof-of-work with Byzantine consensus}
Recent research has developed a class of hybrid systems which uses proof-of-work (PoW) for committee election,
and Byzantine consensus algorithms to agree on transactions.
% And then they use a Byzantine consensus algorithm to actually reach consensus on a set of transactions within the committee.
Some examples are SCP~\cite{luu2015scp}, ByzCoin~\cite{kogias2016enhancing} and Solidus~\cite{abraham2016solidus}.

@@

\subsection{Sharding}

Sharding is a technique to achieve horizontal scalability by grouping nodes into multiple committees, also known as shards.
Nodes within a single shard run a Byzantine consensus algorithm to agree on a set of transactions that belong to that specific shard.
An intra-shard protocol is needed for transactions that involve nodes from more than one shard.
The number of shards grows linearly with respect to the total computational power in the network.
This scheme achieves horizontal scalability because if every shard commits transactions at the same throughput,
then adding more shard would naturally result in a linear increase of global throughput.
Examples of blockchain systems that use sharding are Elastico~\cite{luu2016elastico} and OmniLedger~\cite{kokoris2017omniledger}.

The biggest limitation of sharding is that it is only optimal if transactions stay in the same shard.
In fact, Elastico cannot atomically process inter-shard transactions.
OmniLedger has an inter-shard transaction protocol but choosing a good shard size is difficult.
A large shard size would make the system less scalable because the Byzantine consensus algorithm must be run by a large number of nodes.
A small shard size would result in a large number of inter-shard transactions which also hinder scalability.
The authors of OmniLedger noted that inter-shard transactions have significantly higher latency compared to the consensus protocol~\cite{kokoris2017omniledger}.
Furthermore, since no shards can be compromised for the system to function correctly,
the adversaries have more opportunities to compromise the system.

@@

Tangle~\cite{tangle}, Corda~\cite{corda} and the original TrustChain~\cite{multichain} do not use global consensus at all.
In these schemes, every node has their own chain.
Transactions between nodes are recorded on their respective chains.
This effectively results in a directed acyclic graph.
By avoiding global consensus, this approach achieves extremely desirable scalability properties similar to BitTorrent~\cite{cohen2003incentives}.

@@

We saw in~\Cref{sec:taxonomy} that the majority of the systems cannot achieve horizontal scalability.
To the best of our knowledge, only two systems---Elastico~\cite{luu2016elastico} and OmniLedger~\cite{kokoris2017omniledger}---have experimentally demonstrated horizontal scalability.
However, these techniques rely on sharding, thus the performance highly depends on transaction characteristics and the shard size parameter because inter-shard transactions are slow.
Furthermore, all the systems described in~\Cref{sec:taxonomy} are complete blockchain systems designed for a concrete application.
We wish to design a blockchain consensus protocol that can be used in many applications.
For example, the accounting of detailed internet traffic in Tribler~\cite{pouwelse2008tribler, multichain} and decentralised market in Tribler\footnote{\url{https://github.com/Tribler/tribler/blob/devel/Tribler/community/tradechain/__init__.py}}.
Hence our research question is the following.
\begin{displayquote}
\emph{How can we design a blockchain consensus protocol that is fault-tolerant,
horizontally scalable,
and able to reach global consensus?}
\end{displayquote}

@@

\subsection*{Limitations}
Since our consensus protocol is application neutral, it does not attempt to prevent the Sybil attack~\cite{douceur2002sybil}.
A good defence mechanism requires application specific information.
For example, a social network based Sybil defence mechanisms use graph structure of real-world relationships~\cite{yu2006sybilguard}.
Online marketplaces such as Amazon use the rating of buyer and sellers.
% Since our system is application neutral, we do not provide an explicit Sybil defence mechanism.
On the other hand, our system has no restrictions on the Sybil defence mechanism
and applications built on top of our system can use the best mechanism for their purpose.

For the same reason, we do not explicitly consider spam or denial of service attacks.
Without a concrete application, it is difficult to distinguish a super active user from an attacker.

>>>>

We saw that early blockchain systems face a scalability problem.
In particular, the use PoW is unlikely to reach a transaction rate suitable for ubiquitous use.
Many attempts to fix the scalability problem exist in academia as well as the industry.
In this chapter, we describe the related work and identify their limitations.
Then, we state our research question which aims to overcome some of these.

\section{Related work}
\label{sec:taxonomy}

Blockchain research has seen a surge in recent years from both the industry and academia,
this resulted in a myriad of blockchain systems with different approaches to scalability.
To understand the current state-of-the-art,
we classify various block\-chain systems by their scalability approach.

\subsection{Early blockchain systems}
This category represents the baseline,
which are systems with a probabilistic consensus algorithm.
That is, transactions never reach consensus with a probability of 1.
Given sufficient computational power, adversaries are able to undo any transaction.
The typical examples are PoW based systems such as Bitcoin, Ethereum and other Altcoins.
In Bitcoin, nodes compete in solving puzzles.
The first node solves the puzzle has the privilege to create a new block.
The level of consensus of a block containing many transactions is determined by how deep it is in the Bitcoin blockchain,
which is also called the number of confirmation.
The probability of a block being orphaned drops exponentially as the depth increases~\cite{bitcoin}.
Nevertheless, the probability of the highest block being orphaned is non-negligible.

The advantage of this approach is that it can be used in a large network.
In fact, prior to Bitcoin, there was no Internet-scale consensus protocol.
Bitcoin is also fault-tolerant because attackers can not outpace honest users in finding new blocks unless they have a majority of the computational power,
as long as the majority is honest and reasonable measures are taken to prevent the selfish mining attack~\cite{eyal2014majority}.
The disadvantage, however, is that transactions are never in consensus with a probability of 1---no consensus finality.
Hence double spending is possible for transactions that do not have a large number of confirmations.
Furthermore, as we mentioned in~\Cref{ch:intro},
the performance is limited due to the fact that blocks are of fixed size and are generated at fixed intervals.
Thus early blockchain systems do not scale.

@@

Off-chain transaction systems are implemented using multi-signature addresses~\cite{bitcoinmultisig} and hashed time-locked Bitcoin contracts~\cite{bitcointimelock}.
In the simplest case, 
if two parties wish to make frequent transactions,
they open a payment channel in the form of a multi-signature Bitcoin address (for two parties it would be a 2-of-2 signature address).
Each of the party must also deposit some Bitcoins in the multi-signature address,
this is called the opening transaction.
Both parties keep the channel state which is not broadcasted to the network.
The state is updated when the two parties make new transactions.
The protocol disincentivises the parties from broadcasting old channel states.
If this occurs, the counterparty can drain all the Bitcoins in the channel.
To close the channel, the parties simply broadcast the latest net settlement to the Bitcoin network,
this is called the closing transaction.
Effectively, only two transactions need to be broadcasted to the Bitcoin network---the opening and the closing transaction,
even if the two parties made thousands or millions of transactions in between.

The two-party scheme can be extended to a network of channels,
which allows two parties to make off-chain transactions without an open channel as long as they are connected by nodes that do.
For example, if a channel exists between node $A$ and $B$, and a channel exists between node $B$ and $C$,
then $A$ can pay $C$ via the intermediary $B$.
The result is that there is no need to create a payment channel with every node in the network.
If some key nodes, acting as payment hubs, are well-connected,
then nodes can make off-chain transactions to a large number of other nodes by opening only one channel with a payment hub.

@@

This category of systems uses traditional Byzantine consensus algorithms such as PBFT~\cite{castro1999practical}.
In essence, they contain a fixed set of nodes (sometimes called validating peer) that run a Byzantine consensus algorithm to decide on new blocks.
This technique is often used in permissioned systems where the validators must be predetermined,
for example, Hyperledger Fabric~\cite{cachin2016architecture}.

A nice aspect of Byzantine consensus and in particular PBFT is that it can handle much more transactions than classical blockchain systems.
PBFT can, for example, achieve 10,000 TX/s if the number of validating peer is under 16~\cite[Section 5.2]{miller2016honey}.
Further, in contrast to PoW, PBFT consensus is final.
That is, transaction history cannot be re-written if it is already in the blockchain.

@@

\subsection{Combining PoW with Byzantine consensus}
Recent research has developed a class of hybrid systems which uses PoW for committee election,
and Byzantine consensus algorithms to agree on transactions.
% And then they use a Byzantine consensus algorithm to actually reach consensus on a set of transactions within the committee.
Some examples are SCP~\cite{luu2015scp}, ByzCoin~\cite{kogias2016enhancing} and Solidus~\cite{abraham2016solidus}.

@@

\subsection{Sharding}
\label{sec:sharding}

Sharding is a technique to achieve horizontal scalability by grouping nodes into multiple committees, also known as shards.
Nodes within a single shard run a Byzantine consensus algorithm to agree on a set of transactions that belong to that specific shard.
An intra-shard protocol is needed for transactions that involve nodes from more than one shard.
The number of shards grows linearly with respect to the total computational power in the network.
This scheme achieves horizontal scalability because if every shard commits transactions at the same throughput,
then adding more shard would naturally result in a linear increase of global throughput.
Examples of blockchain systems that use sharding are Elastico~\cite{luu2016elastico} and Omni\-Ledger~\cite{kokoris2017omniledger}.

The biggest limitation of sharding is that it is only optimal if transactions stay in the same shard.
In fact, Elastico cannot atomically process inter-shard transactions.
OmniLedger has an inter-shard transaction protocol but choosing a good shard size is difficult.
A large shard size would make the system less scalable because the Byzantine consensus algorithm must be run by a large number of nodes.
A small shard size would result in a large number of inter-shard transactions which also hinder scalability.
The authors of OmniLedger noted that inter-shard transactions have significantly higher latency compared to the consensus protocol~\cite{kokoris2017omniledger}.
Furthermore, using smaller shards is a security risk.
Every shard is fault-tolerant up to at most a third of the shard size.
If the total number of malicious nodes remain fixed, then as the shard size decreases,
it is more probably for a shard to fail.

@@

Tangle~\cite{tangle}, Corda~\cite{corda} and the original TrustChain~\cite{multichain} avoid the need of global consensus.
In these schemes, every node has their own chain.
Transactions between nodes are recorded on their respective chains.
This effectively results in a directed acyclic graph.
By avoiding global consensus, this approach achieves extremely desirable scalability properties similar to BitTorrent~\cite{cohen2003incentives}.

@@

We saw in~\Cref{sec:taxonomy} that the majority of the systems cannot achieve horizontal scalability.
To the best of our knowledge, only the two systems described in~\Cref{sec:sharding} have experimentally demonstrated horizontal scalability.
However, these techniques rely on sharding, thus the performance highly depends on the transaction characteristics and the shard size parameter.
Furthermore, all the systems described in~\Cref{sec:taxonomy} are complete blockchain systems designed for a concrete application.
We wish to design a blockchain consensus protocol that can be used in many applications.
For example, the accounting of detailed internet traffic in Tribler~\cite{pouwelse2008tribler, multichain} and decentralised market in Tribler\footnote{\url{https://github.com/Tribler/tribler/blob/devel/Tribler/community/tradechain/__init__.py}}.
Hence our research question is the following.
\begin{displayquote}
\emph{How can we design a blockchain consensus protocol that is fault-tolerant,
horizontally scalable,
and able to reach global consensus?}
\end{displayquote}

@@

\subsection*{Limitations}
Since our consensus protocol is application neutral, it does not attempt to prevent the Sybil attack~\cite{douceur2002sybil}.
A good defence mechanism requires application specific information.
For example, a social network based Sybil defence mechanisms use random walks in real-world social graphs~\cite{yu2006sybilguard}.
Online marketplaces such as Amazon use the rating of buyer and sellers.
Cryptocurrencies use PoW to vote on the latest block.
% Since our system is application neutral, we do not provide an explicit Sybil defence mechanism.
For the same reason, we do not explicitly consider spam or denial of service attacks 
because without a concrete application,
it is difficult to distinguish a super active user from an attacker.
For this work,
we assume that it is the role of application developer to find a reputation mechanism or a trust model suitable for defending against such attacks.

### 2017-08-21 thesis/chapters/ch3-model.tex
Include genesis block in figures
Thanks Johan

Our system consists of three protocols---the consensus protocol, the transaction protocol and the validation protocol.
It is based on our prior work on TrustChain~\cite{multichain},
where every node independently interacts with each other via their own hash chain\footnote{TrustChain is originally called MultiChain but the name has changed to TrustChain}.

The goal of this chapter is to detail our system specification.
We begin our discussion with an intuitive overview of the architecture in \Cref{sec:system-overview}.
Next, we give the formal description, starting with the model and assumptions in \Cref{sec:model-assumptions}, 
and then the three protocols which make up the complete system.
Finally, we discuss a few variations of our design and their respective tradeoffs in \Cref{sec:tradeoffs}.

\section{System overview}
\label{sec:system-overview}
The architecture is visualised in~\Cref{fig:architecture}.
\begin{figure}[h]
\centering
\includegraphics[width=0.7\textwidth]{architecture}
\caption{Overview of the system architecture}
\label{fig:architecture}
\end{figure}
It consists of one data structure---Extended TrustChain, and three protocols.
The protocols have distinct roles which are evident from their names.
They run concurrently and do not interact with each other.
The only synchronization happens on the Extended TrustChain layer, where all the protocols read and write from it.
We first describe each component individually, starting with Extended TrustChain, and then explain how they fit together.

\subsection*{TrustChain and Extended TrustChain}
Extended TrustChain naturally builds on top of the standard TrustChain. 
Thus we first describe the standard TrustChain.
Our description has a minor difference when compared to the description in~\cite{multichain},
we remark the difference when it occurs.

@@

\begin{figure}
    \includegraphics[width=0.9\textwidth]{trustchain-bad}
    \centering
    \caption{
    A TrustChain example with three nodes.
    Every block is denoted by $t_{i,j}$, where $i$ is the node ID and $j$ is the sequence number of the block.
    The arrows represent hash pointers and the dotted lines represent references.
    The blocks at the ends of the dotted lines are pairs of each other.
    The red block behind $t_{b, 6}$ indicates a fork.}
    \label{fig:trustchain-bad}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.9\textwidth]{trustchain-bad-cp}
    \centering
    \caption{
    An example of Extended TrustChain.
    The circles represent CP blocks,
    they also have hash pointers (arrow) but do not have references (dotted line).
    Note that the sequence number counter do not change, it is shared with TX blocks.}
    \label{fig:trustchain-bad-cp}
\end{figure}

@@

The high communication complexity of Byzantine consensus algorithms prohibits us from running it on a large network.
Thus, at the beginning of every Byzantine consensus algorithm execution,
we randomly elect a set of nodes---called facilitators---to collect CP blocks from every other node and use those blocks as the input to the Byzantine consensus algorithm, and then run it.
After the algorithm completes,
the facilitators output a set of CP blocks which we call the consensus result.
The result is then propagated to the network and the next algorithm execution begins.

>>>>

In this chapter, we break away from the early blockchain paradigm and introduce a novel system that is application neutral,
horizontally scalable and will never have a block size debate.
In particular, our system consists of three protocols---the consensus protocol, the transaction protocol and the validation protocol.
It is based on our prior research on TrustChain~\cite{multichain} at Delft,
where every node independently interacts with each other via their own hash chain\footnote{TrustChain is originally called MultiChain but the name has changed to TrustChain}.

We begin our discussion with an intuitive overview of the architecture in \Cref{sec:system-overview}.
Next, we give the formal description, starting with the model and assumptions in \Cref{sec:model-assumptions}, 
and then the three protocols which make up the complete system.
Finally, we discuss a few variations of our design and their respective tradeoffs in \Cref{sec:tradeoffs}.

\section{System overview}
\label{sec:system-overview}

\begin{figure}[h]
\centering
\includegraphics[width=0.7\textwidth]{architecture}
\caption{Overview of \textsc{Checo} architecture.}
\label{fig:architecture}
\end{figure}

The architecture of \textsc{Checo} is visualised in~\Cref{fig:architecture}.
It consists of one data structure---Extended TrustChain, and three protocols.
The protocols have distinct roles which are evident from their names.
They run concurrently and do not interact with each other.
The only synchronization happens on the Extended TrustChain layer, where all the protocols read and write from it.
We first describe each component individually, starting with Extended TrustChain, and then explain how they fit together.

\subsection*{TrustChain and Extended TrustChain}
We first describe the standard TrustChain and then the Extended TrustChain.
Our description of the standard TrustChain has a minor difference when compared to the description in~\cite{multichain},
we remark the difference when it occurs.

@@

\begin{figure}
    \includegraphics[width=0.9\textwidth]{trustchain-bad}
    \centering
    \caption{
    A TrustChain example with three nodes.
    Every block is denoted by $t_{i,j}$, where $i$ is the node ID and $j$ is the sequence number of the block.
    The arrows represent hash pointers and the dotted lines represent references.
    The blocks at the ends of the dotted lines are pairs of each other.
    The red block behind $t_{b, 6}$ indicates a fork.
    Blocks of index 0 (e.g. $t_{b, 0}$) are genesis blocks.}
    \label{fig:trustchain-bad}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.9\textwidth]{trustchain-bad-cp}
    \centering
    \caption{An example of Extended TrustChain.
    The circles represent CP blocks,
    they also have hash pointers (arrow) but do not have references (dotted line).
    Note that the sequence number counter do not change, it is shared with TX blocks.
    CP blocks of index 0 (e.g. $c_{b, 0}$) are genesis blocks.}
    \label{fig:trustchain-bad-cp}
\end{figure}

@@

The communication complexity of Byzantine consensus algorithms typically grows polynomially w.r.t the number of nodes,
which prohibits us from running it on a large network.
For example, one of the most recent work tested with up to 104 nodes and the algorithm took almost 6 minutes to complete~\cite{miller2016honey}.
Thus, at the beginning of every Byzantine consensus algorithm execution,
we randomly elect a set of nodes---called facilitators---to collect CP blocks from every other node and use those blocks as the input to the Byzantine consensus algorithm, and then run it.
After the algorithm completes,
the facilitators output a set of CP blocks which we call the consensus result.
The result is then propagated to the network and the next algorithm execution begins.

### 2017-08-21 thesis/formalities/abstract.tex
Thanks Johan

\begin{abstract}
% what's the problem?
Blockchain systems have the potential to decentralise many traditionally centralised systems.
However, scalability remains a key challenge.
Without a horizontally scalable solution, blockchain systems remain unsuitable for ubiquitous use.
% what's the solution?
We design a novel blockchain system called \textsc{Checo}.
Each node in our system maintains a personal hash chain,
which only stores transactions that the node is involved in.
A consensus is reached on special blocks called checkpoint blocks rather than on all the transactions.
Checkpoint blocks are effectively a hash pointer to the personal hash chains,
thus a single checkpoint block may represent a large set of transactions.
The consensus protocol does not imply transaction validity.
Hence we introduce a validation protocol which allows nodes to verify that the transactions are correctly recorded,
meaning that consensus on transactions is achieved indirectly via checkpoint blocks.
% how good is the solution?
We evaluate \textsc{Checo} analytically and experimentally.
Our results show a strong indication of horizontal scalability even in the worst case,
where every transaction is made with a randomly selected node.
\end{abstract}

>>>>

\begin{abstract}
% what's the problem?
Blockchain systems have the potential to decentralise many traditionally centralised systems.
However, scalability remains a key challenge.
Without a horizontally scalable solution,
where performance increases by adding more nodes to the system,
blockchain systems remain unsuitable for ubiquitous use.
% what's the solution?
We design a novel blockchain system called \textsc{Checo}.
Each node in our system maintains a personal hash chain,
which only stores transactions that the node is involved in.
A consensus is reached on special blocks called checkpoint blocks rather than on all the transactions.
Checkpoint blocks are effectively a hash pointer to the personal hash chains,
thus a single checkpoint block may represent an arbitrarily large set of transactions.
We introduce a validation protocol so that any node can check the validity of any transaction.
Since it is a point-to-point protocol, we achieve horizontal scalability.
% how good is the solution?
We analytically evaluate our system and proof a number of highly desirable correctness properties.
Further, we give a free and open-source implementation of \textsc{Checo} and evaluate it experimentally.
Our results show a strong indication of horizontal scalability.
\end{abstract}
